---
title: "Naa10-het-combined"
author: "Andrew Garcia"
date: "2023-02-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Naa10 het liver and heart combined
Combined datasets for western blots of heart and liver lysate from
Naa10 het and their WT/WT controls

#Data
```{r}
hetmut <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQcRFHGDVhqvdOCxdt5pc4LOR39VsU25zrWf_R7L8UZx2IYswNd8ONUfBtO4M87tIJD8Wed0HWD2F-Q/pub?gid=0&single=true&output=csv",header = T)

head(hetmut)
```



```{r}
##switched Name and Replicate fromn integers to factors
hetmut$Name <- as.factor(hetmut$Name)
hetmut$Replicate <- as.factor (hetmut$Replicate)
hetmut$Genotype <- as.factor(hetmut$Genotype)
hetmut$Organ <- as.factor(hetmut$Organ)

head(hetmut)

##changed Name and Replicate from integer data to replicate data
```
```{r}
install.packages("ggplot2",
                 repos ="http://cran.us.r-project.org")
```

##distribution of NAA10 signal
```{r}
library(ggplot2)
ggplot(hetmut,aes(x = Genotype,
                 y = Normalized.Signal,
                 color = Name,
                 shape = Replicate))+
  geom_point()+
  ylab("NAA10 signal normalized to
       REVERT total protein stain")+
  ggtitle("NAA10 levels in Naa10
          heterozygous mutant heart")

##if we added jitter as another layer, the data points would be duplicated
##in the resultant plot!
#remove names
```




##Group-mean datasets in dplyr
```{r}
#I am more familiar with using summarySE in Rmisc to generate a dataframe that contains group means


```


#Summary data of Naa10 het heart and hypothesis testing
```{r}

install.packages("Rmisc", repos = "http://cran.us.r-project.org")

```

##Grouping by Genotype and Organ
```{r}
##Summary statistics for Normalized NAA10 signal
##Possible groupings: genotype, replicate, organ
##Replicate grouping pertains to replicate blot grouping

library(Rmisc)
hetmut_sum <- summarySE(hetmut, measurevar="Normalized.Signal", groupvars=c("Genotype","Organ"))

hetmut_sum
```
###plot of organ and genotype group mean
```{r}
ggplot(hetmut_sum, aes(x = Genotype,
                       y = Normalized.Signal,
                       shape = Organ))+
  geom_point()+
  geom_errorbar(aes(ymin = Normalized.Signal - sd,
                ymax = Normalized.Signal + sd))
```


##Genotype group mean
```{r}
##Normalized NAA10 signal is grouped by genotype.
##N = 6 for both genotypes because the 3 biological replicates in each genotype were assayed twice
##this gives me the group mean dataframe that I will need to layer onto the plot of individual observartions

hetmut_sum1 <- summarySE(hetmut, measurevar="Normalized.Signal", groupvars=c("Genotype"))

hetmut_sum1
```



```{r}
#group means plus standards
#essentially looking to plot this onto the individual data plot
ggplot(hetmut_sum1, aes(x = Genotype, y = Normalized.Signal))+
  geom_point()+
  geom_errorbar(aes(ymin = Normalized.Signal - sd,
                ymax = Normalized.Signal + sd))
```

##individual data and group means plot
```{r}
#ggplot(hetmut) plots Normalized.Signal as a function of Genotype
#geom_point plots individual observations on this plot
#geom_errorbar points to my group means df hetmut_sum1 and the bounds of the mean+/- standard error bar
#the successive geom_point plots the mean; specify color so it does not conflict with the color call in the first geom_point

library(ggplot2)

ggplot(hetmut,aes(x = Genotype,
                 y = Normalized.Signal,
                 fill = Organ,
                 alpha = 2.0))+
  geom_point(aes(shape = Organ,
                 color = Name),
             alpha = 2.0,
             size = 2,
             position = position_jitterdodge())+
    geom_boxplot(outlier.shape = NA,
               alpha = 0.1)+
  stat_summary(fun.y = mean, color = "darkred", position = position_dodge(0.75),
             geom = "point", shape = 3, size = 3,
             show.legend = FALSE)+
  xlab("Naa10 genotype")+
  ylab("NAA10 signal normalized to
       REVERT total protein stain")+
  theme_bw(base_size = 12, base_family = "Helvetica")
```


###main fig; Organ fill?
```{r}
library(ggplot2)
ggplot(hetmut,aes(x = Genotype,
                 y = Normalized.Signal,
                 fill = Organ,
                 alpha = 2.0))+
  geom_point(aes(shape = Organ),
             alpha = 2.0,
             size = 2,
             position = position_jitterdodge())+
  geom_boxplot(outlier.shape = NA,
               alpha = 0.1)+
    stat_summary(fun.y = mean, color = "red", position = position_dodge(0.75),
             geom = "point", shape = 3, size = 3,stroke = 1,
             show.legend = FALSE)+
  xlab("Naa10 genotype")+
  ylab("NAA10 signal normalized to
       REVERT total protein stain")+
  theme_bw(base_size = 12, base_family = "Helvetica")
```


#Hypothesis testing
##unpaired t-test
```{r}
t.test(Normalized.Signal~Genotype, hetmut)
```

```{r}
t.test(Normalized.Signal~Organ, hetmut)
```


##Anova
```{r}
install.packages("car", repos = "http://cran.us.r-project.org")
```


```{r}
library(car)

hetmut.aov <- lm(Normalized.Signal~Genotype*Organ, hetmut)

summary(hetmut.aov)
Anova(hetmut.aov, type = "III")
```

```{r}
TukeyHSD(aov(hetmut.aov), conf.level = 0.95)
```

